INSTRUCTIONS FOR PREPARATION AND SUBMISSION OF FULL-PAPERS FOR PUBLICATION IN THE PROCEEDINGS OF XL CILAMCE

### 2020-07-13 CILAMCE/paper_EN.tex
Update CILAMCE LOGO

\begin{figure}[ht!]
\vspace{-50pt}
\flushright
\includegraphics[width=5.5cm]{logoCILAMCE2019.png}
%scale=0.25
\end{figure}

@@

>>>>

\begin{figure}[ht!]
\vspace{-50pt}
\flushright
\includegraphics[width=5.5cm]{logoCILAMCE2020.png}
%scale=0.25
\end{figure}

@@

\hypertarget{data-preparation}{%
\subsection{Data preparation}\label{data-preparation}}

The preparation of the data consisted of transforming the sample set in
order to maintain only relevant data for the subsequent studies. Data
that were considered irrelevant or that had the potential to add
undesirable noise to the analysis were removed. In addition, the
relevant data has been transformed to better fit the studies in the next
steps.

\hypertarget{initial-data-cleaning}{%
\subsubsection{Initial data cleaning}\label{initial-data-cleaning}}

Initially, there were 25 duplicate samples that were removed, resulting
in a new total of 1005 samples.

The data show the variables in the columns and samples in the rows.
However it was found that some samples are identical in proportions of
ingredients, changing only the value of age and compressive strength,
for example, samples 653, 654, 678 and 681, shown in the Table
\ref{tab:similar-samples}.

\caption{\label{tab:similar-samples}Samples with same composition}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{cccccccccc}
\toprule
\multicolumn{1}{c}{ID} & \multicolumn{1}{c}{Cement} & \multicolumn{1}{c}{B.F.S.} & \multicolumn{1}{c}{Fly ash} & \multicolumn{1}{c}{Water} & \multicolumn{1}{c}{Superp.} & \multicolumn{1}{c}{C.Aggregate} & \multicolumn{1}{c}{F.Aggregate} & \multicolumn{1}{c}{Day} & \multicolumn{1}{c}{Comp.Str.} \\
 & $kg/m^3$ & $kg/m^3$ & $kg/m^3$ & $kg/m^3$ & $kg/m^3$ & $kg/m^3$ & $kg/m^3$ &  & $MPa$\\
\midrule
653 & 102 & 153 & 0 & 192 & 0 & 887 & 942 & 3 & 4.57\\
\addlinespace
678 & 102 & 153 & 0 & 192 & 0 & 887 & 942 & 7 & 7.68\\
\addlinespace
681 & 102 & 153 & 0 & 192 & 0 & 887 & 942 & 28 & 17.28\\
\addlinespace
654 & 102 & 153 & 0 & 192 & 0 & 887 & 942 & 90 & 25.46\\
\bottomrule
\end{tabular}}
\end{table}

In addition, there are also samples with the same values and proportions
of ingredients, but with different compressive strength, probably due to
differences in the building process. This is the case, for example, of
samples 472, 473 and 474, shown in the table
\ref{tab:similar-samples-2}.
